---
title: "Rapid Assessment Protocol: Photo Randomizer Script"
author: "Sam McNeely"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Step 1: Install and load packages

Before beginning any randomization of photos and sites for unbiased scoring, we need to install the necessary packages and load them into the current session so that their functions can be used.

We can accomplish this in a single *if-else* statement explained below:
  
  A)  If the package **writexl** is NOT currently installed in your package
      library,install the package and then load it into the current session. Using
      the function `require()`, we can make check if **writexl** is installed 
      through a conditional statement. The `!` before `require()` reverses the 
      boolean value `require()` generates without the `!`. For example, if 
      `require(writexl)` is TRUE, then `!require(writexl)` is FALSE.
  B)  If the package **writexl** is currently installed in your package library, 
      then `!require(writexl)` will be FALSE. A FALSE condition in the *if-else*
      statement skips to the *else* section and runs the code inside it: 
      `library(writexl)`.

```{r, message = FALSE, warning = FALSE}
if(!require(writexl)){
  install.packages("writexl")
  library(writexl)
} else {
  library(writexl)
}
```

Follow the same format for the `tidyverse` package.

```{r, message = FALSE, warning = FALSE}
if(!require(tidyverse)){
  install.packages("tidyverse")
  library(tidyverse)
} else {
  library(tidyverse)
}
```
